Comparison to Christensen et al. 2018

### 2023-09-16 paper_comparison/paper-comparison.Rmd
temporary move of paper comparison
move vignette out of folder and rbuildignore it

---
title: "Comparison to Christensen et al. 2018"
author: "Renata Diaz, Juniper Simonis, and Hao Ye"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison to Christensen et al. 2018}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  run_models: FALSE
  rmarkdown.html_vignette.check_title: FALSE
---

@@

![plot of chunk unnamed-chunk-10](./output/lda_distances.png)

@@

![plot of chunk plot_paper_LDA](figure/plot_paper_LDA-1.png)

@@

![plot of chunk plot_LDATS_LDA](figure/plot_LDATS_LDA-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts](figure/plot_paper_LDA_and_LDATS_cpts-1.png)

@@

![plot of chunk plot_ldats_LDA_and_LDATS_cpt](figure/plot_ldats_LDA_and_LDATS_cpt-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts2](figure/plot_paper_LDA_and_LDATS_cpts2-1.png)

@@

![plot of chunk unnamed-chunk-19](./output/paper_paper_cpt_plot.png)

@@

![plot of chunk plot_LDATS_lda_and_paper_cpt2](figure/plot_LDATS_lda_and_paper_cpt2-1.png)

@@

![plot of chunk unnamed-chunk-20](./output/ldats_paper_cpt_plot.png)

>>>>

---
title: "Comparison to Christensen et al. 2018"
author: "Renata Diaz, Juniper Simonis, and Hao Ye"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison to Christensen et al. 2018}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  run_models: FALSE
---

@@

<div class="figure">
<img src="./output/lda_distances.png" alt="plot of chunk unnamed-chunk-10" width="1067" />
<p class="caption">plot of chunk unnamed-chunk-10</p>
</div>

@@

![plot of chunk plot_paper_LDA](plot_paper_LDA-1.png)

@@

![plot of chunk plot_LDATS_LDA](plot_LDATS_LDA-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts](plot_paper_LDA_and_LDATS_cpts-1.png)

@@

![plot of chunk plot_ldats_LDA_and_LDATS_cpt](plot_ldats_LDA_and_LDATS_cpt-1.png)

@@

![plot of chunk plot_paper_LDA_and_LDATS_cpts2](plot_paper_LDA_and_LDATS_cpts2-1.png)

@@

<div class="figure">
<img src="./output/paper_paper_cpt_plot.png" alt="plot of chunk unnamed-chunk-19" width="1067" />
<p class="caption">plot of chunk unnamed-chunk-19</p>
</div>

@@

![plot of chunk plot_LDATS_lda_and_paper_cpt2](plot_LDATS_lda_and_paper_cpt2-1.png)

@@

<div class="figure">
<img src="./output/ldats_paper_cpt_plot.png" alt="plot of chunk unnamed-chunk-20" width="1067" />
<p class="caption">plot of chunk unnamed-chunk-20</p>
</div>
